Reproducible development environments with rix

### 2025-02-20 paper.qmd
typos

keywords: [reproducibility, R, Nix]
keywords-formatted: [reproducibility, "[R]{.proglang}", " [Nix]{.pkg}"]

@@

```
let
  pkgs = import (fetchTarball 
    "https://github.com/NixOS/nixpkgs/archive/976fa336....tar.gz"
  ) {};
  system_packages = builtins.attrValues {
    inherit (pkgs) [R]{.proglang};
  };
in
  pkgs.mkShell {
    buildInputs = [ system_packages ];
    shellHook = "R --vanilla";
  }
```

>>>>

keywords: [reproducibility, R, Nix]
keywords-formatted: [reproducibility, "[R]{.proglang}", "[Nix]{.pkg}"]
number-sections: true

@@

```
let
  pkgs = import (fetchTarball
    "https://github.com/NixOS/nixpkgs/archive/976fa336....tar.gz"
  ) {};
  system_packages = builtins.attrValues {
    inherit (pkgs) R;
  };
in
  pkgs.mkShell {
    buildInputs = [ system_packages ];
    shellHook = "R --vanilla";
  }
```
